On centrality of orthogonal $\Kt$

### 2016-05-01 paper.tex
Minor

It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is a commutative local ring and $\Phi$ has rank $\geq 2$, see \cite{St73}.
We refer to the latter statement as the ``centrality of $\Kt$''.
In~\cite{vdK} using the technique called ``another presentation'' W. van~der~Kallen has shown that the centrality of $\Kt$ holds for $\Phi=\rA_\ell$, $\ell\geq 3$ and arbitrary commutative ring $R$.
Using similar ideas Tulenbaev in~\cite{Tul0} has further generalised van~der~Kallen's result to associative rings that are module-finite over their centres.

>>>>

It is classically known that $\Kt(\Phi, R)$ is a central subgroup of $\St(\Phi, R)$ if $R$ is a commutative local ring and $\Phi$ has rank $\geq 2$, see \cite{St73}.
We refer to the latter statement as the ``centrality of $\Kt$''.
In~\cite{vdK} using the technique called ``another presentation'' W. van~der~Kallen has shown that the centrality of $\Kt$ holds for $\Phi=\rA_\ell$, $\ell\geq 3$ and arbitrary commutative ring $R$.
Using similar ideas Tulenbaev in~\cite{Tul0} further generalised van~der~Kallen's result to associative rings that are module-finite over their centres.
